### 2019-05-28 manuscript/elife/cover-letter/main.tex
Added eLife cover letter

April 29, 2019

@@

Nature Plants

@@

Enclosed please find an electronic copy of the manuscript entitled \textit{“Sting nematodes modify metabolomic profiles of host plants”} for consideration in Nature Plants.  In this manuscript, we present novel data showing that nematode ectoparasites of plants can modify host metabolomes.  While previous work on root-knot and cyst nematode has demonstrated that nematode endoparasites of plants alter metabolite expression, this is the first work documenting a migratory ectoparasite (with a very different lifestyle and co-evolutionary history) extensively modifying host metabolomes.  Specifically, sting nematodes alter global metabolomic profiles in susceptible, moderately tolerant, and tolerant African bermudagrass cultivars through suppression of amino acids (in contrast to endoparasites which upregulate amino acid production) and stimulation of plant defense pathways.  We show that pipecolic acid, a systemic acquired resistance regulator, likely plays a key role in mediating tolerance to sting nematode infection.

@@

This manuscript may likely be of interest to Guillaume Tena as a possible suggested associate editor. The authors have not had prior discussions with the Nature Plants Editorial Board Members about this work.  We suggest the following experts in the field as possible peer reviewers:

>>>>

May 29, 2019

@@

eLife

@@

Enclosed please find an electronic copy of the manuscript entitled \textit{“Sting nematodes modify metabolomic profiles of host plants”} for consideration in eLife.  In this manuscript, we present novel data showing that nematode ectoparasites of plants can modify host metabolomes.  While previous work on root-knot and cyst nematode has demonstrated that nematode endoparasites of plants alter metabolite expression, this is the first work documenting a migratory ectoparasite (with a very different lifestyle and co-evolutionary history) extensively modifying host metabolomes.  Specifically, sting nematodes alter global metabolomic profiles in susceptible, moderately tolerant, and tolerant African bermudagrass cultivars through suppression of amino acids (in contrast to endoparasites which upregulate amino acid production) and stimulation of plant defense pathways.  We show that pipecolic acid, a systemic acquired resistance regulator, likely plays a key role in mediating tolerance to sting nematode infection.

@@

This manuscript may likely be of interest to Guillaume Tena as a possible suggested associate editor. The authors have not had prior discussions with the eLife Editorial Board Members about this work.  We suggest the following experts in the field as possible peer reviewers:
